Malacology: A Programmable Storage System

### 2016-10-18 paper/paper.tex
mantle: add benchmarks to paper
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

>>>>

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-balancer-profiles.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
load balancing interface alleviates load for multiple sequencers in
resource-constrained environments.  ``Underloaded (Baseline)'' is the
throughput of one sequencer running alone on a cluster; the other curves show
how load balancing affects the throughput of one sequencer when sequencers for
other logs are initially co-located on the same physical server (i.e. an
"Overloaded" environment).}\label{fig:mantle-seq-thruput}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics{figures/mantle-modes.png}
\caption{[\href{https://github.com/double-blind-submitter/osdi16}{source}] The
load balancing interface alleviates load for multiple sequencers in
resource-constrained environments.  ``Underloaded (Baseline)'' is the
throughput of one sequencer running alone on a cluster; the other curves show
how load balancing affects the throughput of one sequencer when sequencers for
other logs are initially co-located on the same physical server (i.e. an
"Overloaded" environment).}\label{fig:mantle-seq-thruput}
\end{figure}
